### 2012-10-10 Docs/getting_started/getting_started.tex
updates to directory structure

In \maestro, each problem lives under one of three sub-directories of
{\tt MAESTRO/}: {\tt SCIENCE/}, {\tt TEST\_PROBLEMS/}, or {\tt
UNIT\_TESTS/}.  This problem sub-directory will contain any
problem-specific files as well as the {\tt GNUmakefile} that specifies
how to build the executable.  Note: we rely on features of GNU {\tt
make}.  Full details of the {\tt GNUmakefile} can be found
in \S~\ref{sec:adding_problems}.  Here we will configure for a serial
build.

Change directory to {\tt MAESTRO/TEST\_PROBLEMS/test2/}.    
We only need to worry about the options at the very top of the
{\tt GNUmakefile} for now.  These should be set as follows:
\begin{itemize}
\item {\tt NDEBUG := t}

@@

Different problems in \maestro\ are contained in one of three
sub-directories under {\tt MAESTRO/} ({\tt SCIENCE/}, {\tt
TEST\_PROBLEMS/}, or {\tt UNIT\_TESTS/}).  The {\tt GNUmakefile} in each
problem directory lists the components of {\tt MAESTRO} that are used
to build the executable.  {\tt TEST\_PROBLEMS/} contains simple
problems that were used in the development of \maestro.  Many
of these were featured in the papers describing the \maestro\ algorithm.

Some of the test problems available are:
\begin{itemize}
\item {\tt flame} \\[-3mm]

The {\tt flame} problem models a planar laminar flame.  Initially cool
fuel and hot ash are put in pressure equilibrium.  Thermal diffusion
transfers heat to the fuel, driving a burning front.  This problem
does not use the traditional \maestro\ elliptic constraint, but
rather enforces $\nabla \cdot U = S$ (through the runtime parameter
{\tt do\_smallscale = T}) as discussed in \cite{SNe}.

\item {\tt spherical\_heat} \\[-3mm]

{\tt spherical\_heat} maps a spherical star (a Chandrasekhar-mass white
dwarf) onto the Cartesian domain and uses an external heat source to
cause the star to expand.  This is the 3D analogue of the {\tt
  test\_basestate} unit test (see \S~\ref{chapter:unit_tests}).  This
problem was discussed in \cite{multilevel}.

@@

\item {\tt test\_spherical} \\[-3mm]

{\tt test\_spherical} sets up an isentropically stratified star
and stirs it up with a random velocity field.  The low Mach number
constraint is replaced with the anelastic constraint (through
the {\tt beta\_type} runtime parameter).  Analytically, under
these conditions, the density of the star should not change.
This test problem was discussed in \cite{lowMach4}.

>>>>

In \maestro, each problem lives under one of three sub-directories of
{\tt MAESTRO/Exec}: {\tt SCIENCE/}, {\tt TEST\_PROBLEMS/}, or {\tt
UNIT\_TESTS/}.  This problem sub-directory will contain any
problem-specific files as well as the {\tt GNUmakefile} that specifies
how to build the executable.  Note: we rely on features of GNU {\tt
make}.  Full details of the {\tt GNUmakefile} can be found
in \S~\ref{sec:adding_problems}.  Here we will configure for a serial
build.

Change directory to {\tt MAESTRO/Exec/TEST\_PROBLEMS/test2/}.    
We only need to worry about the options at the very top of the
{\tt GNUmakefile} for now.  These should be set as follows:
\begin{itemize}
\item {\tt NDEBUG := t}

@@

Different problems in \maestro\ are contained in one of three
sub-directories under {\tt MAESTRO/Exec}: ({\tt SCIENCE/}, {\tt
TEST\_PROBLEMS/}, or {\tt UNIT\_TESTS/}).  The {\tt GNUmakefile} in each
problem directory lists the components of {\tt MAESTRO} that are used
to build the executable.  {\tt TEST\_PROBLEMS/} contains simple
problems that were used in the development of \maestro.  Many
of these were featured in the papers describing the \maestro\ algorithm.

Some of the test problems available are:
\begin{itemize}
\item {\tt incomp\_shear\_jet} \\[-3mm]

A simple pure-incompressible shear layer problem.  This is the example
problem used in \cite{bellcolellaglaz}.  This is useful to see how to
use \maestro\ as an incompressible solver.

@@

\section{Distributed Science Problems}

The following problems were used for science studies.  It is
anticipated that more will be made available with time.

\item {\tt toy\_convect} \\[-3mm]

A nova-like problem for studying convection.  This problem has seen
extensive use in understanding which prediction types are the best
when we have sharp species gradients.  See Mike Z or Ryan for details.

\item {\tt wdconvect} \\[-3mm]

Model convection leading up to ignition in the Chandraseskhar-mass SNe
Ia progenitor model.  This setup was the basis for the simulations
presented in \cite{lowMach4,wdconvect,wdturb}.
